Mass and occupation fraction of dark matter halos hosting Lyman-$\alpha$ emitters at $z\sim 3$

### 2013-11-08 paper/ms.tex
minor updates

\begin{enumerate}
\item The first is the SSA22
field of $1.38$ deg$^2$ with $1394$ detected LAEs (7 sub-fields), this
field has been known to harbor a region with a large density excess of
galaxies. {\bf It is important to note  that the first sub-field of this sample  is
exactly the same that are reported by \cite{Hayashino2004} } as it is reported 
by as by \cite{Yamada2012}  in section $2.1$.

@@

{\bf The second constraint is the angular correlation function
(ACF). {\bf \cite{Yamada2012} does not report an ACF measurement for
    the entire field. Instead we use the results by
  \cite{Hayashino2004} who has reported the ACF in the SSA22 region,
  including its densest subfield.}

In adition to Hayashino's ACF we use as a matter of comparison the
ACF reported by  \cite{Ouchi2008}. This ACF is computer over
an observed field of 1 deg$^2$ over the SXDS field, which is twice
 as large as the SXDS region observed by \cite{Yamada2012}.

There are some differences between \cite{Ouchi2008} observations and those by
\cite{Yamada2012}. The details in the color selection, corresponding
limiting luminosities and EW thresholds are different in these
references. Nevertheless we use the ACF from this particular to 
get a sense of a mean ACF but do not use it to constrain our parameter space. }

%{\bf The LAEs number density inferred by \cite{Hayashino2004} is
 % $0.37$ arcmin$^{-2}$, which is $15\%$ lower than the new measurement
%by \cite{Yamada2012}.

{\bf In the case of \cite{Ouchi2008} the number
density is $0.10$ arcmin$^{-2}$, which is $\sim 50\%$ than the value
inferred by \cite{Yamada2012} for a portion of the same region.}

@@

{\bf The field centered on SSA22 has been known to harbor a 
  galaxy overdensity. Measurements of Lyman Break Galaxies show that
  the densest sub-field presents an overdensity 6 times the one present in a
  blank field \cite{XXX}. Using the data of \cite{Yamada2012}, we
  compute that for LAEs the whole region is only 1.4 times more dense than
  the blank fields of SXDS, SDF and GOODS-N. The densest sub-field
  in SSA22 is 2 times denser than the average of the blank
  fields.}

{\bf Excluding the densest region in the SSA22, all the fields have a
similar number density as the blank fields and cannot be considered
as rare. The left panel in Figure \ref{fig:halos} shows the integrated
distribution of LAEs number density in all the fields reported in
\cite{Yamada2012}. It is evident that there is only one sub-field that
stands out as an outlier in the distribution (it corresponds to the
densest field in SSA22), the central message of this distribution is
that all the other fields form a continous distribution in number density.}

{\bf Therefore, using
as a benchmark the number density distribution that includes the
sub-fields in the SSA22 region does not impose a strong bias to select
very rare regions in a cosmological simulation. However, on has to
keep in mind that only very rarely the full number density distribution from a
simulation will include a very dense field as an outlier. We will not
require the presence of such field to judge a mock distribution as
successful. In terms of the ACF the results that include the densest
field in SSA22 \citep{Hayashino2004} are consistent, within the
uncertainties, with the results of other fields \citep{Ouchi2008}.}

@@

The second constraint  comes from the angular correlation function (ACF)
for all the models having the $15$ mock surveys consistent with
observations . The ACF is computed using 
the Landy \&  Szalay estimator \citep{Landy1993}  on two different 
fields in the mock survey. The first field is the densest to be compared
against the results of \cite{Hayashino2004}. The second field
has an average number density and is compared against \cite{Ouchi2010}.

>>>>

\begin{enumerate}
\item The first is the SSA22
field of $1.38$ deg$^2$ with $1394$ detected LAEs (7 sub-fields), this
field has been known to harbor a region with a large density excess of
galaxies. {\bf The first sub-field of is taken around the same region
  observed in \cite{Hayashino2004} } as it is reported  by as by
\cite{Yamada2012} in section $2.1$.

@@

{\bf A secondary benchmark is the angular correlation function
(ACF). \cite{Yamada2012} does not report an ACF measurement for
  the entire field. Instead we use the results by
  \cite{Hayashino2004} who has reported the ACF in the SSA22 region,
  including its densest subfield. In adition to Hayashino's ACF we use
  as a matter of comparison the ACF reported by
  \cite{Ouchi2008}. This ACF is computer over an observed field of 1
  deg$^2$ over the SXDS field.}

{\bf There are some differences between \cite{Ouchi2008} observations
  and those by \cite{Yamada2012}. The details in the color selection,
  corresponding limiting luminosities and EW thresholds are different
  in these references. The average LAEs number density inferred by
  \cite{Hayashino2004} is   $0.37$ arcmin$^{-2}$, which is $15\%$
  lower than the new measurement by \cite{Yamada2012}. In the case of
  \cite{Ouchi2008} the number density is $0.10$ arcmin$^{-2}$, which
  is $\sim 50\%$ higher than the value inferred by \cite{Yamada2012}
  for a portion of the same region.}

{\bf In spite of being different fields, we find that the parameters
  describing this

the parameters in their
  correlation function are consistent with each other Nevertheless we use the ACF from this
  particular to  get a sense of a mean ACF.

@@

{\bf The field SSA22 has been known to harbor a significant
  galaxy overdensity. \cite{Yamada2012} estimates that the densest
  subfield is likely to be a rare density peak with $3-4\sigma$
  significance on the scale of $\sim 60$\hMpc.}

{\bf Excluding that high density sub-field in SSA22, all the fields
  are average with a similar number density as the blank fields
  rare. The left panel in Figure \ref{fig:halos} shows the integrated distribution of LAEs number density in all the fields reported in
  \cite{Yamada2012}. It is evident that there is only one sub-field that
  stands out as an outlier in the distribution (it corresponds to the
  densest field in SSA22). All the other fields form a continous
  distribution in number density.}

{\bf Therefore, using the whole SSA22 region as a benchmark in the
  number density distribution does not impose any bias. However, on
  has to  keep in mind that is not plausible that the full number
  density distribution from a simulation will include a very dense
  field. The statistical test we perform to compare mock distributions against
  observations does not require such a perfect match.

We will not
  require the presence of such field to judge a mock distribution as
  successful. In terms of the ACF the results that include the densest
  field in SSA22 \citep{Hayashino2004} are consistent, within the
  uncertainties, with the results of other fields \citep{Ouchi2008}.}

@@

The second constraint  comes from the angular correlation function (ACF)
for all the models having the $15$ mock surveys consistent with
observations .

{\bf The ACF is computed using  the Landy \&  Szalay estimator
  \citep{Landy1993}  on two different  fields in the mock survey. The
  first field is the densest to be compared against the results of
  \cite{Hayashino2004}. The second field has an average number density and is compared against \cite{Ouchi2010}.}
